---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Codes Description

<!-- badges: start -->

<!-- badges: end -->

The goal of mrJ2R is to obtain the proposed estimators to evaluate the average treatment effect (ATE) under jump-to-reference (J2R) based on the paper **Multiply robust estimators in longitudinal studies with missing data under control-based imputation**.

## Installation

You can install the development version of rpsftmPDT from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("siyi48/mrJ2R")
```

## Usage

In the cross-sectional study, the main function `jtr.1time` provides the ATE estimator.

```{r}
library(mrJ2R)
data <- dat1
formula.om <- y ~ z1 + z2 + z3 + z4 + z5 + a +
  a:(z1 + z2 + z3 + z4 + z5)
formula.ps <- a ~ z1 + z2 + z3 + z4 + z5
formula.rp <- r ~ z1 + z2 + z3 + z4 + z5 + a +
  a:(z1 + z2 + z3 + z4 + z5)
mat.cal <- data.matrix(data[,paste0("z", 1:5)]) # calibration matrix
res.1time <- jtr.1time(formula.ps = formula.ps,
                       formula.rp = formula.rp,
                       formula.om = formula.om,
                       data = data, mat.cal = mat.cal,
                       type = c("tr", "tr.cal", "rpom"))
res.1time
```


In the longitudinal study, the main function `jtr.longi` provides the ATE estimator.
```{r}
data <- dat2
formula.om <- list()
formula.om[[2]] <- y2 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) +
  x5 + gam::s(y1)
formula.om[[1]] <- y1 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) + x5

formula.ps <- list()
formula.ps[[2]] <- a ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) +
  x5  + gam::s(y1)
formula.ps[[1]] <- a ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) + x5

formula.rp <- list()
formula.rp[[2]] <- r2 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) +
  x5 + gam::s(y1)
formula.rp[[1]] <- r1 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) + x5

formula.pm <- list()
formula.pm[[2]] <- y2 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) +
  x5 + gam::s(y1)
formula.pm[[1]] <- y1 ~ gam::s(x1) + gam::s(x2) + gam::s(x3) + gam::s(x4) + x5

# create a list of matrices for calibration
k <- 5
inter_mat <- matrix(0, nrow = nrow(data), ncol = choose(k-1, 2)+k-1)
count <- 1
for(i in 1:(k-1)){
  for(j in i:(k-1)){
    inter_mat[,count] <- data[,k+i]*data[,k+j]
    count <- count + 1
  }
}
list.cal <- list()
list.cal[[1]] <- cbind(data.matrix(data[,k + 1:k]), inter_mat) # A
list.cal[[2]] <- cbind(cbind(list.cal[[1]], data$a)) # R1
list.cal[[3]] <- cbind(list.cal[[2]], data$y1,
                       data.matrix(data[,k + 1:(k-1)])*data$y1, data$y1^2) # R2

res.longi <- jtr.longi(formula.ps = formula.ps,
                       formula.rp = formula.rp,
                       formula.om = formula.om,
                       formula.pm = formula.pm,
                       list.cal = list.cal,
                       data = data,
                       type = c("mr", "mr.cal", "rppm"))
res.longi
```
