---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Codes Description

<!-- badges: start -->

<!-- badges: end -->

The goal of mrJ2R is to obtain the proposed estimators to evaluate the average treatment effect (ATE) under jump-to-reference (J2R) based on the paper **Multiply robust estimators in longitudinal studies with missing data under control-based imputation**.

## Installation

You can install the development version of rpsftmPDT from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
# devtools::install_github("siyi48/mrJ2R")
```

## Usage

In the cross-sectional study, the main function `jtr.1time` provides the ATE estimator

```{r}
library(mrJ2R)
data <- dat1
formula.om <- y ~ z1 + z2 + z3 + z4 + z5 + a +
  a:(z1 + z2 + z3 + z4 + z5)
formula.ps <- a ~ z1 + z2 + z3 + z4 + z5
formula.rp <- r ~ z1 + z2 + z3 + z4 + z5 + a +
  a:(z1 + z2 + z3 + z4 + z5)
mat.cal <- data.matrix(data[,paste0("z", 1:5)]) # calibration matrix
res.1time <- jtr.1time(formula.ps = formula.ps,
                       formula.rp = formula.rp,
                       formula.om = formula.om,
                       data = data, mat.cal = mat.cal,
                       type = c("tr", "tr.cal", "rpom"))
res.1time
```




